---
title: "Class-Presentation"
author: "Kenney Snell"
date: "December 22, 2017"
output: 
   html_document:
      keep_md: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## My New Slide

```{r,comment="",echo=FALSE,fig.align='center',fig.cap="My Awesome Figure"}

plot(mtcars$wt,mtcars$mpg,xlab = "Weight",ylab = "MPG")
```
Plain text

*italized text*

**Bold text**

`for (i %in% 1:10)`


Some comment

## My title

- Bullet one
- Bullet two

1. Item a
2. Item b

### A Top level subheading

#### A second level subheading


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

