---
title: "Week3 Developing Data Products"
author: "Kenney Snell"
date: "January 1, 2018"
output: html_document 
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Date: January 1, 2018
##US economic time series

Description

    This dataset was produced from US economic time series data available from 
    http://research.stlouisfed.org/fred2. economics is in "wide" format, economics_long is in "long"
    format.

economics_long:    Format

date: Month of data collection

psavert: personal savings rate, http://research.stlouisfed.org/fred2/series/PSAVERT/

pce:
    personal consumption expenditures, in billions of dollars,  
    http://research.stlouisfed.org/fred2/series/PCE

unemploy:
    number of unemployed in thousands, http://research.stlouisfed.org/fred2/series/UNEMPLOY

uempmed:
    median duration of unemployment, in weeks, http://research.stlouisfed.org/fred2/series/UEMPMED

pop:
    total population, in thousands, http://research.stlouisfed.org/fred2/series/POP

```{r plot econ,message=FALSE}
library(plotly)
library(caret)
data(economics_long)
set.seed(101)
plot_ly (x=economics_long$date,y=economics_long$value, color = economics_long$variable)
```

